### 2021-11-23 input/proposal.tex
not much

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that the functioning of epidemic propagation is
well-aligned with the objectives of scoped broadcast. More precisely,
it underlines the transitive relevance of messages, thus a \process
can stop forwarding messages as soon as its predicate becomes
unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.
%
We use \NAMEB to efficiently modify the state of each \process
depending on the partitions that exist in the system.

@@

\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
    $\implies\eventually$CP]
    % 
    Assuming reliable communication links
    ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually
    reach consistent partitioning if each \process delivers its best
    message among \underline{r}eceived messages $R_x$, and forwards
    its best message among \underline{d}elivered messages $D_x$.
    % , \ie
    % the message $\alpha_s^d$ with the smallest distance $d$ to the
    % source $s$
    % ($(\alpha_s^d = \min R_x) \implies (d_x(\alpha_s^d) \wedge
    % f_x(\TODO{\alpha_s^d}))$).
\end{theorem}

@@

  \noindent Whenever a \process $s$ becomes a source, it delivers its
  own message $d_s(\alpha_{s})$. Whatever its set of received
  messages, its own partition $P_s$ becomes and remains its closest
  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq s: |\Pi_{s
    s}| < |\Pi_{s x}|$.
  %
  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification
  $\forall \langle s, y \rangle \in E \iff \eventually
  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
  received messages, every \process $q$ in this neighborhood such that
  there exists no closer source $s'$ than the received one $s$,
  delivers it, since $|\Pi_{sq}| < |\Pi_{s'q}|$.
  %
  \noindent They forward it and their respective neighbors eventually
  receive it. By transitivity, the message originating from $s$
  reaches all \processes belonging to $P_s$ at least through their
  shortest paths: $\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s})$.  Since there
  exists only one best sum of weights per \process that can never be
  retracted, \processes eventually reach consistent partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values piggybacked in messages and
  accumulated over forwarding,
\item \processes only add new partitions to the system,
\item and \processes never join, crash nor leave the system.
\end{inparaenum}
For the sake of simplicity, a \process does not forward a notification
to its sender (Line~\ref{line:accumulator}).  Figure~\ref{fig:add}
illustrates the behavior of this algorithm on a system comprising 4
\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
become the sources of their partition.  They \NAMEB a notification
\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
does not improve its partition distance. \Processes $c$ and $d$ will
never acknowledge that Source~$a$ exists. Ultimately, \processes
discard last transiting messages. Despite the obvious lack of traffic
optimization, the system reaches consistent partitioning.

>>>>

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that the functioning of epidemic propagation is
well-aligned with the objectives of scoped broadcast. More precisely,
it underlines the transitive relevance of messages, thus a \process
can stop \TODO{forwarding messages} as soon as its predicate becomes
unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.
%
We use \NAMEB to efficiently modify the state of each \process
depending on the partitions that exist in the system.

@@

\begin{theorem}[\label{theo:efb}\underline{F}orwarding of \underline{B}est (FB)
    $\implies\eventually$CP]
    % 
    Assuming reliable communication links
    ($s_{xy}(m) \iff \eventually r_{yx}(m)$), \processes eventually
    reach consistent partitioning if each \process delivers its \TODO{best}
    message among \underline{r}eceived messages $R_x$, and forwards
    its \TODO{best} message among \underline{d}elivered messages $D_x$.
    % , \ie
    % the message $\alpha_s^d$ with the smallest distance $d$ to the
    % source $s$
    % ($(\alpha_s^d = \min R_x) \implies (d_x(\alpha_s^d) \wedge
    % f_x(\TODO{\alpha_s^d}))$).
\end{theorem}

@@

  \noindent Whenever a \process $s$ becomes a source, it delivers its
  own message $d_s(\alpha_{s})$. Whatever its set of received
  messages, its own partition $P_s$ becomes and remains its closest
  partition $\alpha_{s}^{|\Pi_{ss}|} = \min D_s$ since $\forall x \neq
  s: |\Pi_{s s}| < |\Pi_{s x}|$.
  %
  \noindent Such a source $s$ forwards $\alpha_{s}$ to its neighbors.
  Since communication links are reliable, neighboring \processes
  eventually receive such a notification
  $\forall \langle s, y \rangle \in E \iff \eventually
  r_y(\alpha_{s}^{d})$. Most importantly, whatever the order of
  received messages, every \process $q$ in this neighborhood such that
  there exists no closer source $s'$ than the received one $s$,
  delivers it, since $w_{sq} < |\Pi_{s'q}|$.
  %
  \noindent They forward it and their respective neighbors eventually
  receive it. By transitivity, the message originating from $s$
  reaches all \processes belonging to $P_s$ at least through their
  shortest paths: $\smash{\forall q' \in V, s, s' \in S: |\Pi_{s q'}| <
  |\Pi_{s' q'}| \implies \eventually d_{q'}(\alpha_{s}^{|\Pi_{sq'}|})}$.
  Since there exists only one best sum of weights per \process that
  can never be retracted, \processes eventually reach consistent
  partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values piggybacked in messages and
  accumulated over forwarding,
\item \processes only add new partitions to the system,
\item and \processes never join, crash nor leave the system.
\end{inparaenum}
For the sake of simplicity and to remove obvious loops, a \process
does not forward a notification to its sender
(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
behavior of this algorithm on a system comprising 4 \processes $a$,
$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
their partition.  They \NAMEB a notification \underline{a}dd message:
$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
it improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. \Processes $c$ and $d$ will never acknowledge that
Source~$a$ exists. Ultimately, \processes discard last transiting
messages. Despite the obvious lack of traffic optimization, the system
reaches consistent partitioning.
